# Fonts

This chapters displays the different fonts and their shapes.
Partly to visualise them, partly to highlight problems with specific combinations of characters.

```{r}
#| label: setup
library(lipsum)
set.seed(20200817)
header <- function(words = 4, format = FALSE) {
  sprintf(
    ifelse(
      format,
      "%s '%s' `%s` _%s_ **%s**",
      "%s %s %s %s %s"
    ),
    lipsum::sentence(words = words),
    lipsum::sentence(words = words),
    lipsum::sentence(words = words),
    lipsum::sentence(words = words),
    lipsum::sentence(words = words)
  )
}
```

## Normal

ABCDEFHIJKLMNOPQRSTUVWXYZ abcdefghijklmonopqrstuvwxyz €$£ @&#§µ^ ()|²³<>/\_*+- ,;:.?!~ äàáâã ëèéê ïìíî öòóô üùúû ÿ ç ñ ÄÀÁÂ ËÈÉÊ ÏÌÍÎ ÖÒÓÔ ÜÙÚÛ Ñ 0123456789 <!-- spell-check: ignore-->

`r paragraph(n = 1)`

quotation marks: "double", 'single'

## Bold

**ABCDEFHIJKLMNOPQRSTUVWXYZ abcdefghijklmonopqrstuvwxyz €$£ @&#§µ^ ()[]{}|²³<>/\\\_\*+- ,;:.?!~ äàáâã ëèéê ïìíî öòóô üùúû ÿ ç ñ ÄÀÁÂ ËÈÉÊ ÏÌÍÎ ÖÒÓÔ ÜÙÚÛ Ñ 0123456789** <!-- spell-check: ignore-->

**`r paragraph(n = 1)`**

**quotation marks: "double", 'single'**

## Italics

_ABCDEFHIJKLMNOPQRSTUVWXYZ abcdefghijklmonopqrstuvwxyz €$£ @&#§µ^ ()[]{}|²³<>/\\\_\*+- ,;:.?!~ äàáâã ëèéê ïìíî öòóô üùúû ÿ ç ñ ÄÀÁÂ ËÈÉÊ ÏÌÍÎ ÖÒÓÔ ÜÙÚÛ Ñ 0123456789_ <!-- spell-check: ignore-->

_`r paragraph(n = 1)`_

_quotation marks: "double", 'single'_

## Bold italics {#sec-bold-italic}

**_ABCDEFHIJKLMNOPQRSTUVWXYZ abcdefghijklmonopqrstuvwxyz €$£ @&#§µ^ ()[]{}|²³<>/\\\_\*+- ,;:.?!~ äàáâã ëèéê ïìíî öòóô üùúû ÿ ç ñ ÄÀÁÂ ËÈÉÊ ÏÌÍÎ ÖÒÓÔ ÜÙÚÛ Ñ 0123456789_** <!-- spell-check: ignore-->

_**`r paragraph(n = 1)`**_

_**quotation marks: "double", 'single'**_

## Fixed width font

```{r}
#| label: fixed-plain
#| results: "asis"
cat("`", paragraph(), "`", sep = "")
```

`quotation marks: "double", 'single'`

```{r}
#| label: fixed-bold
#| results: "asis"
cat("**`", paragraph(), "`**", sep = "")
```

**`quotation marks: "double", 'single'`**

80 characters fit within the margins of the pdf

`12345678911234567892123456789312345678941234567895123456789612345678971234567898`

**`12345678911234567892123456789312345678941234567895123456789612345678971234567898`**

100 characters no longer fit on the pdf page

`1234567891123456789212345678931234567894123456789512345678961234567897123456789812345678991234567890`

**`1234567891123456789212345678931234567894123456789512345678961234567897123456789812345678991234567890`**

## Distinguish similar looking characters

|                            | normal | bold | italics | bold italic | fixed width |
| ---------------------------| --- | --- | --- | --------- | --------- |
| small L versus capital i   | lI | **lI** | _lI_ | **_lI_** | `lI` **`lI`** | <!-- spell-check: ignore-->
| capital O versus number 0  | O0 | **O0** | _O0_ | **_O0_** | `O0` **`O0`** |
